### 2024-05-30 thesis/input_files/data_exploratory.tex
corrected chapter 7

\section{GEFCom2014}
The first class of datasets we identified are the ones from the GEFCom2014 competition. The data is freely hosted on Dr.\ Hong's blog \cite{hong2016probabilistic}.
The main reason is that, these datasets are considered an excellent test case for comparing predictive models between the EF community. Additionally, the scores of the competing models are freely available, this enables us to carry out a clean and transparent comparative study.
The GEFCom2014 consisted of four tracks: price, load, wind power and solar power forecasting. 
The GEFCom2014 folder contains a zip file for each of the four tracks.
We provide forecasts for the load and price quantities.
\\
\subsection{GEFCom2014 price track}
In the price forecasting track, the goal was to predict the electricity price for the next 24 hours of a single zone. 
The data can be found in the GEFCom2014-P\_V2 zip file alongside a set of instructions and the benchmark forecasts.
This data consists of time series for the locational marginal price, for the zonal load and for the system load. The data covers the time interval ranging from the $1^{st}$ of January 2011 to the $15^{th}$ of June 2013, see Figure \ref{fig:price_track_fig1}.\ 
Additionally, as the competition went on, the real observed data of the previous tasks were made available.
The fifteen target days ordered by task number are: 16/06/2013, 17/06/2013, 24/06/2013, 04/07/2013, 09/07/2013, 13/07/2013, 16/07/2013, 18/07/2013, 19/07/2013, 20/07/2013, 24/07/2013, 25/07/2013, 07/12/2013, 08/12/2013. 
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/price_track_fig1.png}
    \caption{Price track GEFCom2014}
    \label{fig:price_track_fig1}
\end{figure}
\subsubsection{EDA}
In exploring this data we started off by plotting the time series of the zonal prices alongside with the total load and zonal load, see Figure \ref{fig:price_track_fig1}.
After that, we plotted the scatter plot for inspecting the correlation between the predictors and the dependent variables, Figure \ref{fig:gefcom_zonal_price_vs_zonal_load} and Figure \ref{fig:gefcom_zonal_price_vs_total_load}. From these visualisations, we can see their goodness for predicting zonal prices since there exists a clear correlation between the candidate predictors and the target variables.

>>>>

\section{GEFCom2014}
The first class of datasets we identified are the ones from the GEFCom2014 competition. The data is freely hosted on Dr.\ Hong's blog \cite{hong2016probabilistic}.
The main reason is that, these datasets are considered an excellent test case for comparing predictive models between the EF community. Additionally, the scores of the competing models are freely available, this enables us to carry out a clean and transparent comparative study.
The GEFCom2014 consisted of four tracks: price, load, wind power and solar power forecasting. 
The GEFCom2014 folder contains a zip file for each of the four tracks.
We provide forecasts for the load and price quantities.
\\
\subsection{GEFCom2014 price track}
In the price forecasting track, the goal was to predict the electricity price for the next 24 hours of a single zone. 
The data can be found in the GEFCom2014-P\_V2 zip file alongside a set of instructions and the benchmark forecasts.
This data consists of time series for the locational marginal price, for the zonal load and for the system load. The data covers the time interval ranging from the $1^{st}$ of January 2011 to the $15^{th}$ of June 2013, see Figure \ref{fig:price_track_fig1}.\ 
Additionally, as the competition went on, the real observed data of the previous tasks were made available.
The fifteen target days ordered by task number are: 16/06/2013, 17/06/2013, 24/06/2013, 04/07/2013, 09/07/2013, 13/07/2013, 16/07/2013, 18/07/2013, 19/07/2013, 20/07/2013, 24/07/2013, 25/07/2013, 07/12/2013, 08/12/2013, 17/12/2013. 
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/price_track_fig1.png}
    \caption{Price track GEFCom2014}
    \label{fig:price_track_fig1}
\end{figure}
\subsubsection{EDA}
In exploring this data we started off by plotting the time series of the zonal prices alongside with the total load and zonal load, see Figure \ref{fig:price_track_fig1}.
After that, we plotted the scatter plot for inspecting the correlation between the predictors and the dependent variables, Figure \ref{fig:gefcom_zonal_price_vs_zonal_load} and Figure \ref{fig:gefcom_zonal_price_vs_total_load}. From these visualisations, we can see their goodness for predicting zonal prices since there exists a clear correlation between the candidate predictors and the target variables.

### 2024-05-30 thesis/input_files/probabilistic.tex
corrected chapter 7

% In our implementatiton we take the point that minsimizes the distance between the boundary of domain of alpha, in this way we are guaranteed we do not take ith index of alpha_i for retrieving b, because it that case it would not work.
%contribution is implementation kernel quantile regression for pythos users since there exists only r version
\subsection{Weather quantiles}
In order to get acquainted with the inner workings of the presented methods, this section covers an application explaining practical details and comparing results.
\\
The dataset used is the Melbourne daily maximum temperatures \citeW{hdrcde}. It contains the daily maximum temperatures in Melbourne, Australia, from 1981-1990, excluding leap days, see Figure \ref{fig:melbourne_temperature_data}.
Due to the bimodality of the data, such dataset is commonly used to give a difficult quantile regression problem \cite{hyndman1996estimating}, thus why we chose it. The observed bimodality is that a hot day is likely to be followed by either an equally hot day or one much cooler.
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/melbourne_temperature.png}
    \caption{Melbourne temperatures dataset}
    \label{fig:melbourne_temperature_data}
\end{figure}
Hereafter, the results of the four presented methods on the Melbourne dataset are reported, see Figure \ref{fig:melbourne_quantiles_comparison} for a visualisation. Notice, the kernel considered here is the Gaussian RBF. Hyperparameters have been tuned through cross validation, see Appendix \ref{appendix:cross_validation}.
\begin{figure}[!h]
    \begin{subfigure}[b]{0.5\linewidth}
      \centering
      \includegraphics[width=1.1\textwidth]{images/melbourne_linear_quantile_regression.png} 
      \caption{Linear quantile regression} 
      \label{fig:melbourne_linear_quantile_regression} 
      \vspace{4ex}
    \end{subfigure}%% 
    \begin{subfigure}[b]{0.5\linewidth}
      \centering
      \includegraphics[width=1.1\textwidth]{images/melbourne_gradient_boosting_quantile_regression.png} 
      \caption{Gradient boosting quantile regression} 
      \label{fig:melbourne_gradient_boosting_quantile_regression} 
      \vspace{4ex}
    \end{subfigure} 
    \begin{subfigure}[b]{0.5\linewidth}
      \centering
      \includegraphics[width=1.1\textwidth]{images/melbourne_quantile_forest.png} 
      \caption{Quantile forest} 
      \label{fig:melbourne_quantile_forest} 
    \end{subfigure}%%
    \begin{subfigure}[b]{0.5\linewidth}
      \centering
      \includegraphics[width=1.1\textwidth]{images/melbourne_kernel_quantile_regression.png}
      \caption{Kernel quantile regression, Gaussian RBF} 
      \label{fig:melborune_kernel_quantile_regression} 
    \end{subfigure} 
    \caption{Quantile regressors comparison Melbourne weather data}
    \label{fig:melbourne_quantiles_comparison} 
  \end{figure}

% tables
\begin{table}[!h]
\caption{Pinball loss of Melbourne data}
\begin{tabular}{lllll}
    \toprule
     & Linear qr & Gbm qr & Quantile forest & KQR \\
    \midrule
    Pinball loss & 11.278895 & 10.317612 & 10.340842 & \textbf{10.031708} \\
    \bottomrule
    \end{tabular}
\end{table}

\begin{table}[!h]
    \caption{Pinball loss quantile-wise of Melbourne data}
    \begin{tabular}{lllll}
    \toprule
    Quantiles & Linear qr & Gbm qr & Quantile forest & KQR \\
    \midrule
    0.100000 & 0.710644 & 0.549232 & 0.562888 & \textbf{0.540235} \\
    0.200000 & 1.155014 & 0.938561 & 0.946712 & \textbf{0.903213} \\
    0.300000 & 1.417805 & 1.212671 & 1.222407 & \textbf{1.173803} \\
    0.400000 & 1.540108 & 1.399925 & 1.409293 & \textbf{1.367943} \\
    0.500000 & 1.574957 & 1.517281 & 1.484589 & \textbf{1.455849} \\
    0.600000 & 1.525114 & 1.498608 & 1.495474 & 1.\textbf{447470} \\
    0.700000 & 1.397918 & 1.372183 & 1.362173 & \textbf{1.331503} \\
    0.800000 & 1.170140 & 1.115077 & 1.123195 & \textbf{1.096606} \\
    0.900000 & 0.787195 & \textbf{0.714075} & 0.734112 & 0.715085 \\
    \bottomrule
    \end{tabular}
\end{table}
As already pointed out, the quantile regression with $q=0.5$ corresponds to the standard regression problem, hence we can compare the proposed methods also in terms of the mean absolute error.
\begin{table}[!h]
\caption{Mean absolute error of Melbourne data}
\begin{tabular}{lllll}
    \toprule
     & Linear qr & Gbm qr & Quantile forest & KQR \\
    \midrule
    MAE & 3.253882 & 3.134805 & 3.095041 & \textbf{3.024336} \\
    \bottomrule
    \end{tabular}
\end{table}  
From these tables, we can see that kernel quantile regression outperformes the simple quantile regressor as well as the more complex models like quantile forest and gradient boosting quantile regression for the Melbourne temperatures dataset. Not only kernel quantile regression was the best in terms of total pinball loss but also the best in terms of each quantile pinball loss and mean absolute error.
Comparison has been carried out on further datasets, yielding similar conclusions as the one of above, to know more see Appendix \ref{appendix:quantile_regressor_extensive_comparison}.

@@

% tables
\begin{table}[!h]
    \caption{Kernels comparison pinball loss for Melbourne data}
    \label{tab:kernel pinball comparison}
    \begin{center}
    \begin{tabular}{lll}
        \toprule
        & Kernel & Pinball loss
        \\
        \midrule
        & Gaussian RBF &  10.031708 \\
        & Absolute Laplacian &  10.056884 \\
        & Gauss RBFx Absolute Laplacian & 10.150826 \\
        & Cosine & 16.253973    \\
        & Linear & 10.463867    \\
        & Polynomial & 10.089147     \\
        & Sigmoid & 16.253973            \\
        & Chi squared & \textbf{10.023732}       \\
        & Matern 0.5 & 10.056883  \\
        & Matern 1.5 & 10.040288  \\
        & Matern 2.5 & 10.024495    \\
        & Periodic  & 15.946272\\
        \bottomrule
        \end{tabular}
    \end{center}
    \end{table}

\begin{table}[!h]
    \caption{Kernels comparison pinball loss quantile-wise for Melbourne data}
    \label{tab:kernel pinball comparison quantile-wise}
    \begin{adjustbox}{width=\textwidth}
    \begin{tabular}{lllllllllll}
    \toprule
    Kernel/Quantiles & 0.1 & 0.2 & 0.3 & 0.4 & 0.5 & 0.6 & 0.7 & 0.8 & 0.9 \\
    \midrule
    Gauss RBF &  \textbf{0.540145} &
    0.903193 &
    1.173627 &
    1.368022 &
    1.456053 &
    1.447470 &
    1.331375 &
    1.096649 &
    0.715013 \\
    Laplacian &  0.542499 &
    0.906517 &
    1.177309 &
    1.371198 &
    1.462111 &
    1.453119 &
    1.340193 &
    1.095991 &
    0.707947 \\
    Gauss RBFxLaplacian &0.545787 &
    0.915559 &
    1.189965 &
    1.387109 &
    1.479901 &
    1.475541 &
    1.350803 &
    1.101151 &
    \textbf{0.704922} \\
    Cosine & 0.755479 &
    1.343973 &
    1.802603 &
    2.123425 &
    2.307123 &
    2.367123 &
    2.262603 &
    1.971644 &
    1.320411 \\
    Linear &  0.565663 &
    0.947889 &
    1.250009 &
    1.437863 &
    1.506723 &
    1.478379 &
    1.358865 &
    1.135702 &
    0.782660   \\
    Polynomial &   0.542573 &
    0.908681 &
    1.178357 &
    1.362351 &
    1.450249 &
    1.455228 &
    1.339822 &
    1.107768 &
    0.744118  \\
    Sigmoid &   0.755479 &
    1.343973 &
    1.802603 &
    2.123425 &
    2.307123 &
    2.367123 &
    2.262603 &
    1.971644 &
    1.320411          \\
    Chi squared &   0.541430 &
    0.906352 &
    1.173164 &
    \textbf{1.358862} &
    \textbf{1.444130} &
    \textbf{1.440915} &
    1.332140 &
    1.100262 &
    0.726625     \\
    Matern 0.5 &  0.542499 &
    0.906517 &
    1.177309 &
    1.371198 &
    1.462111 &
    1.453119 &
    1.340193 &
    1.095991 &
    0.707947 \\
    Matern 1.5 &  0.541410 &
    0.902901 &
    1.173943 &
    1.371218 &
    1.462212 &
    1.449296 &
    1.333655 &
    \textbf{1.095092} &
    0.710560 \\
    Matern 2.5 &  0.541233 &
    \textbf{0.902231} &
    \textbf{1.172001} &
    1.366449 &
    1.456505 &
    1.444124 &
    \textbf{1.331251} &
    1.095674 &
    0.715029 \\
    Periodic  & 0.759452 &
    1.352747 &
    1.809921 &
    2.125765 &
    2.314718 &
    2.379657 &
    2.274711 &
    1.976768 &
    1.328630 \\
    \bottomrule
    \end{tabular}
    \end{adjustbox}
\end{table}

\begin{table}[!h]
    \caption{Kernels comparison mean absolute error Melbourne data}
    \label{tab:kernel mae comparison}
    \begin{center}
    \begin{tabular}{lll}
        \toprule
         & Kernel & MAE \\
        \midrule
        & Gauss RBF &  3.024336 \\
        & Laplacian &  3.038633 \\
        & Gauss RBFxLaplacian &  3.070812\\
        & Cosine &    4.849589 \\
        & Linear &     3.142352\\
        & Polynomial &     3.064472 \\
        & Sigmoid &      4.849589       \\
        & Chi squared &    3.022778    \\
        & Matern 0.5 &  3.038633 \\
        & Matern 1.5 &  3.023060 \\
        & Matern 2.5 &  \textbf{3.021949} \\
        & Periodic  & 4.880673 \\
        \bottomrule
        \end{tabular}
    \end{center}
    \end{table}

@@

\begin{figure}[!h]
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melborune_gaussian_rbf_kernel_quantile_regression.png} 
        \caption{Gaussian RBF} 
        \label{} 
        \vspace{4ex}
    \end{subfigure}%% 
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melborune_laplacian_kernel_quantile_regression.png} 
        \caption{Laplacian} 
        \label{} 
        \vspace{4ex}
    \end{subfigure} 
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melborune_gaussian_rbf_x_laplacian_kernel_quantile_regression.png} 
        \caption{Gauss RBFxLaplacian} 
        \label{} 
        \vspace{4ex}
    \end{subfigure}%%
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melborune_cosine_kernel_quantile_regression.png}
        \caption{Cosine} 
        \label{} 
        \vspace{4ex}
    \end{subfigure} 
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melborune_linear_kernel_quantile_regression.png}
        \caption{Linear} 
        \label{} 
        \vspace{4ex}
    \end{subfigure} 
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melborune_polynomial_kernel_quantile_regression.png}
        \caption{Polynomial} 
        \label{} 
        \vspace{4ex}
    \end{subfigure} 
    \end{figure}

\begin{figure}[!h]\ContinuedFloat
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melborune_sigmoid_kernel_quantile_regression.png}
        \caption{Sigmoid} 
        \label{} 
        \vspace{4ex}
    \end{subfigure} 
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melborune_chi_squared_kernel_quantile_regression.png}
        \caption{Chi squared} 
        \label{} 
        \vspace{4ex}
    \end{subfigure}

    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melborune_matern_0.5_kernel_quantile_regression.png}
        \caption{Matern 0.5} 
        \label{} 
        \vspace{4ex}
    \end{subfigure} 
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melborune_matern_1.5_kernel_quantile_regression.png}
        \caption{Matern 1.5} 
        \label{} 
        \vspace{4ex}
    \end{subfigure}

    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melborune_matern_2.5_kernel_quantile_regression.png}
        \caption{Matern 2.5} 
        \label{} 
    \end{subfigure} 
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melborune_periodic_kernel_quantile_regression.png}
        \caption{Periodic} 
        \label{} 
    \end{subfigure} 
    \caption{Kernel quantile regressors comparison for Melbourne data}
    \label{fig:kernel quantile regressors comparison} 
\end{figure}

>>>>

% In our implementatiton we take the point that minsimizes the distance between the boundary of domain of alpha, in this way we are guaranteed we do not take ith index of alpha_i for retrieving b, because it that case it would not work.
%contribution is implementation kernel quantile regression for pythos users since there exists only r version
\subsection{Weather quantiles}
In order to get acquainted with the inner workings of the presented methods, this section covers an application explaining practical details and comparing results.
\\
The dataset used is the Melbourne daily maximum temperatures \citeW{hdrcde}. It contains the daily maximum temperatures in Melbourne, Australia, from 1981-1990, excluding leap days, see Figure \ref{fig:melbourne_temperature_data}.
Due to the bimodality of the data, such dataset is commonly used to give a difficult quantile regression problem \cite{hyndman1996estimating}, thus why we chose it. The observed bimodality is that a hot day is likely to be followed by either an equally hot day or one much cooler.
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{images/melbourne_temperature.png}
    \caption{Melbourne temperatures dataset}
    \label{fig:melbourne_temperature_data}
\end{figure}
Hereafter, the results of the four presented methods on the Melbourne dataset are reported, see Figure \ref{fig:melbourne_quantiles_comparison} for a visualisation. Notice, the kernel considered here is the Gaussian RBF. Hyperparameters have been tuned through cross validation, see Appendix \ref{appendix:cross_validation}.
\begin{figure}[!h]
    \begin{subfigure}[b]{0.5\linewidth}
      \centering
      \includegraphics[width=1.1\textwidth]{images/melbourne_linear_quantile_regression.png} 
      \caption{Linear quantile regression} 
      \label{fig:melbourne_linear_quantile_regression} 
      \vspace{4ex}
    \end{subfigure}%% 
    \begin{subfigure}[b]{0.5\linewidth}
      \centering
      \includegraphics[width=1.1\textwidth]{images/melbourne_gradient_boosting_quantile_regression.png} 
      \caption{Gradient boosting quantile regression} 
      \label{fig:melbourne_gradient_boosting_quantile_regression} 
      \vspace{4ex}
    \end{subfigure} 
    \begin{subfigure}[b]{0.5\linewidth}
      \centering
      \includegraphics[width=1.1\textwidth]{images/melbourne_quantile_forest.png} 
      \caption{Quantile forest} 
      \label{fig:melbourne_quantile_forest} 
    \end{subfigure}%%
    \begin{subfigure}[b]{0.5\linewidth}
      \centering
      \includegraphics[width=1.1\textwidth]{images/melbourne_gaussian_rbf_kernel_quantile_regression.png}
      \caption{Kernel quantile regression, Gaussian RBF} 
      \label{fig:melborune_kernel_quantile_regression} 
    \end{subfigure} 
    \caption{Quantile regressors comparison Melbourne weather data}
    \label{fig:melbourne_quantiles_comparison} 
  \end{figure}

% tables
\begin{table}[!h]
\caption{Pinball loss of Melbourne data}
\begin{tabular}{lllll}
    \toprule
     & Linear qr & Gbm qr & Quantile forest & KQR \\
    \midrule
    Pinball loss & 11.278895 & 10.317612 & 10.340842 & \textbf{10.031546} \\
    \bottomrule
    \end{tabular}
\end{table}

\begin{table}[!h]
    \caption{Pinball loss quantile-wise of Melbourne data}
    \begin{tabular}{lllll}
    \toprule
    Quantiles & Linear qr & Gbm qr & Quantile forest & KQR \\
    \midrule
    0.100000 & 0.710644 & 0.549232 & 0.562888 & \textbf{0.540145} \\
    0.200000 & 1.155014 & 0.938561 & 0.946712 & \textbf{0.903193} \\
    0.300000 & 1.417805 & 1.212671 & 1.222407 & \textbf{1.173627} \\
    0.400000 & 1.540108 & 1.399925 & 1.409293 & \textbf{1.368022} \\
    0.500000 & 1.574957 & 1.517281 & 1.484589 & \textbf{1.456053} \\
    0.600000 & 1.525114 & 1.498608 & 1.495474 & \textbf{1.447470} \\
    0.700000 & 1.397918 & 1.372183 & 1.362173 & \textbf{1.331375} \\
    0.800000 & 1.170140 & 1.115077 & 1.123195 & \textbf{1.096649} \\
    0.900000 & 0.787195 & \textbf{0.714075} & 0.734112 & 0.715013 \\
    \bottomrule
    \end{tabular}
\end{table}
As already pointed out, the quantile regression with $q=0.5$ corresponds to the standard regression problem, hence we can compare the proposed methods also in terms of the mean absolute error.
\begin{table}[!h]
\caption{Mean absolute error of Melbourne data}
\begin{tabular}{lllll}
    \toprule
     & Linear qr & Gbm qr & Quantile forest & KQR \\
    \midrule
    MAE & 3.253882 & 3.134805 & 3.095041 & \textbf{3.024305} \\
    \bottomrule
    \end{tabular}
\end{table}  
From these tables, we can see that kernel quantile regression outperformes the simple quantile regressor as well as the more complex models like quantile forest and gradient boosting quantile regression for the Melbourne temperatures dataset. Not only kernel quantile regression was the best in terms of total pinball loss but also the best in terms of each quantile pinball loss and mean absolute error.
Comparison has been carried out on further datasets, yielding similar conclusions as the one of above, to know more see Appendix \ref{appendix:quantile_regressor_extensive_comparison}.

@@

% tables
\begin{table}[!h]
    \caption{Kernels comparison pinball loss for Melbourne data}
    \label{tab:kernel pinball comparison}
    \begin{center}
    \begin{tabular}{lll}
        \toprule
        & Kernel & Pinball loss
        \\
        \midrule
        & Absolute Laplacian &  10.136551 \\
        & Matern 0.5/Laplacian & 10.136551  \\
        & Matern 1.5 & 10.082668  \\
        & Matern 2.5 & 10.0494190    \\

        & Matern $\infty$/Gaussian RBF &  10.031546 \\

        & Chi squared & \textbf{10.018701}       \\

        & Linear & 10.463752    \\
        & Periodic  & 10.493333\\
        & Polynomial & 10.073935     \\
        & Sigmoid & 10.496149            \\
        % & Gauss RBFx Absolute Laplacian & 10.150826 \\
        & Cosine & 16.254383    \\
        \bottomrule
        \end{tabular}
    \end{center}
    \end{table}

\begin{table}[!h]
    \caption{Kernels comparison pinball loss quantile-wise for Melbourne data}
    \label{tab:kernel pinball comparison quantile-wise}
    \begin{adjustbox}{width=\textwidth}
    \begin{tabular}{lllllllllll}
    \toprule
    Kernel/Quantiles & 0.1 & 0.2 & 0.3 & 0.4 & 0.5 & 0.6 & 0.7 & 0.8 & 0.9 \\
    \midrule
    Absolute Laplacian & 0.545490 &
    0.913866 &
    1.189372 &
    1.386753 &
    1.477606 &
    1.468567 &
    1.348241 &
    1.101059 &
    \textbf{0.705598} &
    \\
    Matern 0.5/Laplacian & 0.545490 &
    0.913866 &
    1.189372 &
    1.386753 &
    1.477606 &
    1.468567 &
    1.348241 &
    1.101059 &
    \textbf{0.705598} &
\\
    Matern 1.5 & 0.542709 &
    0.904605 &
    1.184761 &
    1.382041 &
    1.468031 &
    1.459695 &
    1.338982 &
    1.096042 &
    0.705803 &
  \\  
    Matern 2.5 & 0.541228 &
    0.902478 &
    1.175042 &
    1.374289 &
    1.465790 &
    1.453434 &
    1.334173 &
    \textbf{1.093902} &
    0.709083 &
    \\
    Matern $\infty$/Gaussian RBF & \textbf{0.540145} &
    \textbf{0.903193} &
    1.173627 &
    1.368022 &
    1.456053 &
    1.447470 &
    1.331375 &
    1.096649 &
    0.715013 &    
    \\
    Chi squared & 0.540200 &
    0.904170 &
    \textbf{1.170647} &
    \textbf{1.360472} &
    \textbf{1.449636} &
    1.446009 &
    \textbf{1.333024} &
    1.096450 &
    0.718095 &
    \\
    Linear & 0.565663 &
    0.947889 &
    1.250009 &
    1.437863 &
    1.506723 &
    1.478379 &
    1.358865 &
    1.135702 &
    0.782660 &
    \\
    Periodic & 0.554232 &
    0.930133 &
    1.222068 &
    1.422040 &
    1.518273 &
    1.509894 &
    1.398269 &
    1.160021 &
    0.778402 &
    \\
    Polynomial & 0.542649 &
    0.908764 &
    1.183810 &
    1.370962 &
    1.452645 &
    \textbf{1.442749} &
    1.331137 &
    1.103014 &
    0.738205 &
    \\
    Sigmoid & 0.572588 &
    0.948625 &
    1.244226 &
    1.433785 &
    1.506071 &
    1.480981 &
    1.359103 &
    1.140366 &
    0.810406 &
    \\
    Cosine & 0.755479 &
    1.343973 &
    1.802603 &
    2.123425 &
    2.307123 &
    2.367123 &
    2.262603 &
    1.971644 &
    1.320411 \\
    \bottomrule
    \end{tabular}
    \end{adjustbox}
\end{table}

\begin{table}[!h]
    \caption{Kernels comparison mean absolute error Melbourne data}
    \label{tab:kernel mae comparison}
    \begin{center}
    \begin{tabular}{lll}
        \toprule
         & Kernel & MAE \\
        \midrule
        & Absolute Laplacian &  3.061553 \\
        & Matern 0.5/Laplacian &  3.061553 \\
        & Matern 1.5 &  3.046474 \\
        & Matern 2.5 &  3.034608 \\
        & Matern $\infty$/Gauss RBF &  3.024305 \\
        & Chi squared &    3.027183    \\
        & Linear &     3.142352\\
        & Periodic  & 3.118420 \\
        & Polynomial &     \textbf{3.022743} \\
        & Sigmoid &      3.108107       \\
        & Cosine &    4.849589 \\
        \bottomrule
        \end{tabular}
    \end{center}
    \end{table}

@@

\begin{figure}[!h]
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melbourne_a_laplacian_kernel_quantile_regression.png} 
        \caption{Absolute Laplacian} 
        \label{} 
        \vspace{4ex}
    \end{subfigure}%% 
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melbourne_matern_0.5_kernel_quantile_regression.png} 
        \caption{Matern 0.5/Laplacian} 
        \label{} 
        \vspace{4ex}
    \end{subfigure} 
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melbourne_matern_1.5_kernel_quantile_regression.png} 
        \caption{Matern 1.5} 
        \label{} 
        \vspace{4ex}
    \end{subfigure}%%
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melbourne_matern_2.5_kernel_quantile_regression.png}
        \caption{Matern 2.5} 
        \label{} 
        \vspace{4ex}
    \end{subfigure} 
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melbourne_gaussian_rbf_kernel_quantile_regression.png}
        \caption{Matern $\infty$/Gaussian RBF} 
        \label{} 
        \vspace{4ex}
    \end{subfigure} 
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melbourne_chi_squared_kernel_quantile_regression.png}
        \caption{Chi squared} 
        \label{} 
        \vspace{4ex}
    \end{subfigure} 
    \end{figure}
\begin{figure}[!h]\ContinuedFloat
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melbourne_linear_kernel_quantile_regression.png}
        \caption{Linear} 
        \label{} 
        \vspace{4ex}
    \end{subfigure} 
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melbourne_periodic_kernel_quantile_regression.png}
        \caption{Periodic} 
        \label{} 
        \vspace{4ex}
    \end{subfigure}
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melbourne_polynomial_kernel_quantile_regression.png}
        \caption{Polynomial} 
        \label{} 
        \vspace{4ex}
    \end{subfigure} 
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melbourne_sigmoid_kernel_quantile_regression.png}
        \caption{Sigmoid} 
        \label{} 
        \vspace{4ex}
    \end{subfigure}
    \begin{subfigure}[b]{0.5\linewidth}
        \centering
        \includegraphics[width=1.1\textwidth]{images/melbourne_cosine_kernel_quantile_regression.png}
        \caption{Cosine} 
        \label{} 
    \end{subfigure} 
    \caption{Kernel quantile regressors comparison for Melbourne data}
    \label{fig:kernel quantile regressors comparison} 
\end{figure}
